\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning on Unsecured Trajectories

### 2023-11-29 paper.tex
update

\section{Introduction}\label{sec:introduction}
%Multi-robot systems (MRS) have witnessed increasing adoption in diverse fields, such as warehouse organization, surveillance, forest fire monitoring, and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. The use of MRS offers numerous advantages, but given their distributed nature and reliance on network communication, MRS are particularly vulnerable to cyber threats which introduces new cybersecurity challenges (e.g. unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}). In this paper, we address the specific scenario where attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}. We refer to these restricted regions as \emph{forbidden regions}, which might contain security-sensitive equipment or human workers.

Multi-robot systems (MRS) have found wide applications in various fields, including warehouse organization, surveillance and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. While MRS offers numerous advantages, their distributed nature and dependence on network communication render them vulnerable to cyber threats, introducing new cybersecurity challenges such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}. This paper addresses the specific scenario in which attackers compromise robots and direct them to restricted regions, potentially leading to the exploitation of confidential information, physical property damages, or even human injuries \cite{forrest_2017}. We define these restricted regions as \emph{forbidden regions}, which may contain security-sensitive equipment or human workers.

We focus on countering deliberate deviations, termed \emph{plan-deviation attacks}, identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}. As a security measure, robots perform inter-robot observations using their onboard sensing capabilities. Each robot's self-report includes its own status and additional observations of other robots' status. This mutual observation and reporting establish an observation schedule for the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.

In this paper, we transform the solution to continuous configuration spaces, allowing for more flexible objectives. We provide additional analysis on the reachability of robots to ensure the security of the co-observation schedule. Solving the path optimization problem with constraints based on the sets of locations that the agents could potentially reach, referred to as \emph{reachability regions}, is a novel contribution to the literature.

A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}. Our proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver as a spatio-temporal constraint.

%In this paper, we first transform the solution to continuous configuration spaces and allows for more flexible objectives, providing additional analysis on the reachability of robots in order for the security of co-observation schedule to hold. This problem of solving a path optimization problem with constraints based on the sets of locations that the agents could \emph{potentially} reach, which we call \emph{reachability regions}, has not received attention in the literature.

%A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}. We formulate a way to enforce an empty intersection between forbidden regions and ellipsoidal reachability region while optimizing the trajectory, such that if an attacker takes control of the robots, they cannot perform an undetected attack without breaking the co-observation schedule. Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} in the context of the $\mathtt{RRT^*}$ path planning algorithm, we use an ellipsodial bound to limit the search space and formulated the ellipsoid as the reachability region constraint. In our case, we use a similar bound to optimize the location of the two states to exclude the forbidden region from the ellipsoidal region. We propose a mathematical formulation of reachability regions that is compatible with the solver from  as a spatio-temporal constraint.

This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi,yang2021multi}. Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other. In such case, it is impossible for other robots to get close enough to establish co-observation schedules or find a reachability-secured path. Agent 3 in the Figure \zyang{ref fig:ReachabilitySimulation} is a good example, as it required additional security checkpoint to create secured reachability areas. Secondly, security requirements may come at the cost of overall system performance, as illustrated by the comparison of Figure \zyang{ref fig:trajectories-more-constraint} and \zyang{ref fig:ReachabilitySimulation} where, after the introduction of security constraints, the top left corner is never explored by any robots. This is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems. These challenges are addressed in Chapter \ref{sec:cross-trajectory}, in order to ensure the effectiveness of planning with reachability and co-observation in securing multi-agent systems.

We propose to form \emph{sub-teams} on each route, and setup additional co-observations both within the sub-team and across different sub-teams. Notice that co-observations across sub-teams (named \emph{cross-trajectory co-observation}) are always preferred when feasible, since they provide better security in potential situations where the entire sub-team is compromised.
In this paper, we consider only the high-level path planning, while the assignment of the duties in the team will be performed dynamically as introduced later in later works, making it more difficult for attackers to successfully plan and execute attacks. Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.

@@

\paragraph{Paper contributions} In this paper, we formulate a way to enforce an empty intersection between forbidden region and reachability regions, such that if an attacker takes control of the robots, they cannot perform an undetected attack by entering forbidden regions and meeting co-observation schedules at the same time. The constraints are formulated using an ellipsoidal bound of the reachability region.

We propose to incorporate redundancy in the form of \emph{sub-team}s of multiple robots in place of individual robots along each route. This allows robots to deviate from their assigned sub-team, and join others to perform cross-trajectory co-observations, thereby securing multiple trajectories. We propose a formulation of the multi-flow problem on unsecured MRS trajectories to plan the cross-trajectory co-observations that can preserve the security against plan-deviation attacks.

@@

%Assume that there exists a slowly-time-varying scalar or vector field $\vx$ whose value needs to be estimated at a given number of discrete locations. To explore unknown spatially-distributed fields, autonomous agents are usually required to traverse the entire unknown environment while collecting sensory data to estimate a corresponding map (Figure~\ref{fig:ADMM-example-application}). We model the map as a set of locations of interests arranged on a regular grid, where at each location, we assume that there is a corresponding slowly-time-varying quantity. For our purposes, we are interested in finding paths that best reconstruct the field, i.e., that achieve the minimum uncertainty.

%We address the estimation problem using Kalman Filters (KFs)(cf. \cite{anderson2012optimal}), with a focus on the estimated covariance $P_j$, to calculate the map model uncertainty. We assume the robot provides field measurements at waypoints~$q$, with Gaussian radial basis function modeling radius and quality.
%\rtron{The previous paragraph can be written more compactly.}

@@

To solve the infeasibility problem like the cases shown in \Cref{fig:ReachabilitySimulation} where a secured co-observation schedule cannot be found without external observation approach (Checkpoint at the buttom right of the map), we first use planner (in this paper, an ADMM-based planner introduced in \Cref{sec:ADMM-planning} is used, but other planners are applicable) to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints. Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$. Instead of having the number of robot equal to the number of routes $n_p$, in this section, we assume a total of $n > n_p$ robots are available and organized into \emph{sub-teams} through a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory. \zyang{refrased}Tasking at least one robot to adhere to the reference trajectory to fulfill essential tasks, we capitalize on the presence of additional $n_p-n$ robots to enhance security. These additional robots are initialized to focus are on performing co-observations within their respective sub-teams and

Whenever necessary, they are designed to seamlessly transition between sub-teams. By deviating from their original sub-team's route and joining teams requiring heightened attention, they become instrumental in providing co-observations at critical junctures.

We refer to the new type of co-observations as \emph{cross-trajectory co-observations}. Our objective is to formulate a cross-trajectory co-observation strategy that fortifies an unsecured Multi-Robot System (MRS) trajectory, while minimizing the number of additional robots required.

To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$. 
Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires attention.
The set $E_{q} = E_{t} \union E_{c}$ consists of directed edges connecting $V_i$ to $V_j$ if there exist possible paths between the corresponding locations.  Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general linear programming techniques as specialized solver.

@@

\subsubsection{Checkpoints}\label{sec:security-checkpoint}
Let $q_p\in\real{nT}$ be the MRS trajectory for sub-team $p$ with time horizon $T$, with $q_{p}(t) \in \real{n}$ be the reference waypoint at time $t$. 
\begin{definition}
Checkpoint $v_{pi}=(q_{pi},t_{i})$ is defined as a pair composed of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$ representing a co-observation required for sub-team $p$. 
\end{definition}
For convenience, let $\cI_{v_{i}}$ represent the sub-team that $v_{i}$ belongs to, \zyanghl{Is this necessary?}{and let $q_{v_{pi}} = q_{pi}$, $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$}.

Using the idea of co-observation and reachability constraints introduced in \Cref{sec:ADMM-planning}, we define a set of checkpoints for the trajectory of sub-team $p$ to provide security. \zyang{definition or remark?}

\begin{definition}
The set of $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) that can be used to secure the reference trajectory for sub-team $p$, if the reachability region between consecutive checkpoints $v_{pi}$ and $v_{p(i+1)}$ does not intersect with any of the forbidden areas. The requirement can be formally stated as $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas as $F$. 
\end{definition}

We provide a heuristic approach to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose). The approach is shown in \Cref{alg:checkpoint-gen}, and a toy example is shown in Figure \ref{fig:checkpoint-generate}. 
% We begin by adding the start and end locations $q_{p}(t_{0})$, $q_{p}(t_{e})$ to $V_{q}$, where $t_{0}=0$, and $t_{e}$ is the time horizon. Then, we search for the waypoint $q_{p}(t_{1})$ with the largest $t_{1} \in \{t_{0}, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e. $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$. Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1}, \dots ,t_{2}\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$. $q_{p}(t_{1})$ and $q_{p}(t_{3})$ are then added to $V_{q}$. Afterwards, we set $t_{0}=t_{1}$, $t_{2}=t_{3}$ and repeat the same process. The search is stopped when $t_{0}>t_{2}$, or when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$.

@@

\subsubsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
After identifying checkpoints $\union_p V_p$ for all sub-teams, the next step is to search for cross-trajectory edges connecting all checkpoints to the respective trajectories. 
\rtron{Add definition here for edges to be the counterpart of Definition 8}
These cross-trajectory edges define viable paths between two reference trajectories, allowing robots to closely approach and collaborate with robots on a different reference trajectory for co-observations with the relevant sub-teams. Consequently, at least one endpoint of each edge must correspond to a security checkpoint $v_{p} \in \union_p V_p$. Assuming a single robot is transferred at a time between trajectories, the cross-trajectory edges must adhere to the reachability constraints detailed in ~\Cref{sec:reachability} to ensure that no deviations into forbidden areas can occur during trajectory switches.

@@

\rtron{Move remark about the distributed blocklist here}

@@

With the formulation above, the planning problem can be written as an optimization problem, where the optimization cost balances between the co-observation performance and total number of flows (cross-trajectory robots) needed:
 \begin{subequations} \label{eq:flow-coverage-problem}
     \begin{align}
        \min_{F} & \sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} \label{eq:flow-cost}\\
        s.t. & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij},  \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
        & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1, \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
        & f^k_{ij} \in \{0,1\} \,  \forall (ij)\in E\label{eq:SingleFLowCapacity}
     \end{align}
 \end{subequations}
where, for convenience, we used $(ij)$ to represent the edge $(v_{i},v_{j})$, and $(+i)$ to represent the edge $(v^{+},v_{i})$.

@@

The constant $\rho$ selects the trade-off between the number of surveillance robots and security performance. An increase in robots generally enhancing security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots. %To balance these aspects, the penalty parameter $\rho$ in the cost function \ref{eq:flow-cost} is optimized, achieving an equilibrium between security enhancement and operational efficiency. 
\begin{remark} 
The value of row $\rho$ is upper bounded such that the second term for each single flow in \eqref{eq:flow-cost} is always smaller than one, i.e., $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}\leq 1$. This is because, otherwise \rtron{... explain why the optimal cost would be unbounded}.
\end{remark}

@@

@@

\section{Summary}
In this paper, we provide a method to enhance the security of a multi-robot system without sacrificing the performance. This is done by introducing additional robots to perform cross-trajectory co-observations by traveling between different trajectories. For cases where the secured planning problem is infeasible (or where the user desires to improve the optimality of the trajectories), we model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories. We have shown that the co-observation planning problem across different trajectories can be transformed into a multi-flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.

@@

{\small
\bibliographystyle{unsrt}
\bibliography{ADMM_planning,ACC,tron,ziqi}
}

>>>>

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have found wide applications in various fields, including warehouse organization, surveillance and precision agriculture, owing to their capacity for complex task execution through cooperation and coordination \cite{pajares2015overview, julian2012distributed}. While MRS offers numerous advantages, their distributed nature and dependence on network communication render them vulnerable to cyber threats, introducing new cybersecurity challenges such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}. This paper addresses the specific scenario in which attackers compromise robots and direct them to \emph{forbidden regions}, which may contain security-sensitive equipment or human workers. Such countering deliberate deviations, termed \emph{plan-deviation attacks}, are identified and addressed in previous studies \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola, yang2021multi, yang2020multi}. As a security measure, robots perform inter-robot co-observations using their onboard sensing capabilities to check for unusual behavior. These mutual observation establish an co-observation schedule alongside the path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing forbidden regions) would break the observation plan and be promptly detected.

A preliminary version of the paper was presented at conferences \cite{yang2020multi,yang2021multi}. When extanding the solution from \cite{wardega2019resilience} in grid-world to continuous configuration spaces, additional reachability analysis is erquired for additional security. Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. One typical approach involves computing an over-approximation of the reachable space for checking safety properities. Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric extrapolations, such as zonotopes and ellipsoids, to represent a compact enclosure of the reachability sets. In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions. In contrast, our work shifts the focus to reachability analysis during the planning phase, addressing the path optimization problem by incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}. This contribution adds a novel perspective to the existing literature.

This proposed approach enforces an empty intersection between forbidden regions and an ellipsoidal reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver as a spatio-temporal constraint.

This paper also extend the previous works by fixing two main challenges identified in \cite{wardega2023hola, yang2020multi, yang2021multi}, the feasibility problem and optimality problem. Firstly, finding a co-observation and reachability secured plan may not always be feasible when robots are separated from others by obstacles or forbidden regions, or are located far away from each other. Secondly, security requirements may come at the cost of overall system performance, which is particularly concerning given that system performance is a key factor in the decision to use multi-agent systems. In \Cref{sec:cross-trajectory}, these challenges are addressed through introducing additional robots into the MRS. Robots are formed into \emph{sub-teams} and tasked to follow an optimal trajectory without security constraints. The added redundant robots are then used to setup additional co-observations both within the sub-team and across different sub-teams by deviating from the . Cross-trajectory co-observations allows sub-teams to preserve the optimal unsecured trajectories (as shown in Figure \ref{fig:cross-traj-comparison-set}), as it does not require the entire \emph{sub-team} to maintain a close distance with other teams when co-observation occurs.

@@

\paragraph*{Paper contributions} 
In this paper, two main contributions have been presented.

\begin{itemize}
  \item We present an innovative method to integrate reachability analysis into the ADMM-based optimal trajectory solver for multi-robot systems, preventing attackers from executing undetected attacks by simultaneously entering forbidden areas and adhering to co-observation schedules.
  \item We introduce additional robots to form \emph{sub-teams} for both intra-sub-team and cross-sub-team co-observations. A new co-observation planning algorithm is formulated that can generate a resilient multi-robot trajectory with a co-observation plan that still preserve the optimal performance against arbitrary tasks. We also find the minimum redundant robots required for the security.
\end{itemize}

\paragraph*{paper ourline}
The rest of this paper is organized as follows. In \Cref{sec:ADMM-planning}, we begin by providing an overview of the ADMM-based optimal trajectory solver. We then introduced the ellipsoidal reachability region and formulate it to different constraints with respect to different type of forbidden regions. In \Cref{sec:cross-trajectory}, we proposed the formulation of sub-teams and introduced the planning algorithm of the cross-trajectory co-observation planning problem. Finally, in \Cref{sec:summary}, we provide summary of this paper.

\section{Literature review}
\subsection{Reachability analysis}
Reachability analysis is a common step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. A common method is to compute an over-approximation of the reachable space for checking safety properities. Various researches rely on a geometrical extrapolation of the system states like zonotopes and ellipsoids as representation of a compact enclosure of the reachability sets \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive,maiga2015comprehensive}. The work in \cite{}

@@

@@

To solve the infeasibility problem like the cases shown in \Cref{fig:ReachabilitySimulation} where a secured co-observation schedule cannot be found without external observation approach (Checkpoint at the buttom right of the map), we first use planner (in this paper, an ADMM-based planner introduced in \Cref{sec:ADMM-planning} is used, but other planners are applicable) to generate $n_p$ routes $\{q_p\}_{p=1}^{N_p}$ without reachability and co-observation constraints. Here, the state $q_p(t), p \in\{\cI_0,\ldots,\cI_{p}\}$ represents the reference position of the $i$-th sub-team at time $t\in\{0, \dots, T\}$. Instead of having the number of robot equal to the number of routes $n_p$, in this section, we assume a total of $n > n_p$ robots are available and organized into \emph{sub-teams} through a time-varying partition $\cI(t)=\union_p \cI_p(t)$ where robots in each \emph{sub-team} $\cI_p$ share the same nominal trajectory. \zyang{refrased}Tasking at least one robot to adhere to the reference trajectory to fulfill essential tasks, we capitalize on the presence of additional $n_p-n$ robots to enhance security. These additional robots are initialized to focus are on performing co-observations within their respective sub-teams and whenever necessary, they are designed to deviate from their original sub-team's route and joining teams requiring heightened attention (i.e. travelling near forbidden regions) and providing necessary co-observations. We refer to the new type of co-observations as \emph{cross-trajectory co-observations}. The objective of this section is to formulate a cross-trajectory co-observation strategy that fortifies an unsecured Multi-Robot System (MRS) trajectory, while minimizing the number of additional robots required.

To solve this problem, we model the planned trajectory $\{q_p\}_{p=1}^{N_p}$ as a directed \emph{checkpoint graph} $G_{q}=(V_{q}, E_{q})$. 
Vertices $V_{q}$ are a key locations in $\{q_p\}$ that requires co-observation to achieve security as described in \Cref{rmk:revised-security}. The set $E_{q} = E_{t} \union E_{c}$ consists of directed edges connecting $V_i$ to $V_j$ if there exist possible paths between the corresponding locations.  Inspired by \cite{yu2013multi}, we show that additional robots in the sub-team can be formulated as flows in the checkpoint graph, transforming the co-observation planning problem into a network multi-flow problem that can be solved using general Mixed-Intiger Linear Programming techniques as specialized solver.

@@

\subsubsection{Checkpoints}\label{sec:security-checkpoint}
Let $q_p\in\real{nT}$ be the MRS trajectory for sub-team $p$ with time horizon $T$, with $q_{p}(t) \in \real{n}$ be the reference waypoint at time $t$. We locate checkpoints among $q_p$ that requires co-observations in order for the MRS trajectories to be secured as defined in \Cref{rmk:revised-security}. Checkpoint $v_{pi}=(q_{pi},t_{i})$ is defined as a pair composed of a location $q_{pi}=q_{p}(t_i)$ and a time $t_{i}$ representing a co-observation required for sub-team $p$. 
For convenience, let $\cI_{v_{i}}$ represent the sub-team that $v_{i}$ belongs to, and let $q_{v_{pi}} =q_{pi}$ and $t_{v_{pi}}$ be the corresponding waypoint and time for checkpoint $v_{pi}$.

\begin{remark}
A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if the reachability region between consecutive checkpoints $v_{pi}$ and $v_{p(i+1)}$ does not intersect with any of the forbidden areas. The requirement can be formally stated as $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden areas as $F$. 
\end{remark}

A heuristic approach is provided (\Cref{alg:checkpoint-gen}) to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose) with a toy example shown in Figure \ref{fig:checkpoint-generate}.

@@

\subsubsection{Cross-trajectory edges}\label{sec:cross-traj-edges}
In order for co-observation to happen cross different trajectories at checkpoints, we search for available connection paths (\emph{cross-trajectory edges}) between checkpoints on different trajectories allowing robots deviate from one sub-team to approach, perform co-observation with robots on a different sub-team. 
\begin{remark}
  Cross-trajectory edges $E_c = (v_1, v_2)$ define viable paths between two reference trajectories, where $\cI_{v_1}\neq\cI_{v_2}$ and at least one of $v_1 $ and $v_2$ correspond to a security checkpoint $\union_p V_p$. The cross-trajectory edges must also adhere to the reachability constraints $\mathcal{E}(q_{v_1}, q_{v_2}, t_{v_1},t_{v_2}) \intersect F = \emptyset$ to ensure that no deviations into forbidden areas can occur during trajectory switches.  
\end{remark}

@@

@@

With the formulation above, the planning problem can be written as an optimization problem, where the optimization cost balances between the co-observation performance and total number of flows (cross-trajectory robots) needed:
 \begin{subequations} \label{eq:flow-coverage-problem}
     \begin{align}
        \min_{F} &\sum^{\cK}_{k} \sum_{(+i)\in E} f^{k}_{+i} - \rho \sum^{\cK}_k \sum_{(ij)\in E} w_{ij} f^k_{ij} \label{eq:flow-cost}\\
        s.t. & \sum_{\{h:(hi) \in E\}}f^k_{hi}=\sum_{\{j:(ij) \in E\}}f^k_{ij},  \forall k,\forall v \in V_{q} / \{v^{+}, v^{-}\}  \label{eq:FlowBalanceConstraint}\\
        & \sum^{\cK}_k\sum_{\{i:(ij)\in E \}} f^k_{ij} \geq 1, \forall v_{j} \in \{V^{s}_{p}\} \label{eq:FlowCoverage}\\
        & f^k_{ij} \in \{0,1\} \,  \forall (ij)\in E\label{eq:SingleFLowCapacity}
     \end{align}
 \end{subequations}
where, for convenience, we used $(ij)$ to represent the edge $(v_{i},v_{j})$, and $(+i)$ to represent the edge $(v^{+},v_{i})$.

@@

The constant $\rho$ selects the trade-off between the number of surveillance robots and security performance. An increase in robots generally enhancing security via cross-trajectory co-observations; this also increases the complexity of the coordination across robots.

@@

\begin{remark} 
The value of row $\rho$ is upper bounded such that the second term for each single flow in \eqref{eq:flow-cost} is always smaller than one, i.e., $ \rho \sum_{(ij)\in E} w_{ij} f^k_{ij}\leq 1$. Otherwise, the iteration continues indefinitely as adding additional flow introduce a negative term $\sum_{(+i)\in E} f^{k}_{+i} - \rho\sum_{(ij)\in E} w_{ij} f^k_{ij} = 1- \rho\sum_{(ij)\in E} w_{ij} f^k_{ij}<0$ which always makes the cost \eqref{eq:flow-cost} smaller.
\end{remark}

@@

\section{Summary}\label{sec:summary}
In this paper, we provide a method to enhance the security of a multi-robot system without sacrificing the performance. This is done by introducing additional robots to perform cross-trajectory co-observations by traveling between different trajectories. For cases where the secured planning problem is infeasible (or where the user desires to improve the optimality of the trajectories), we model the unsecured multi-robot trajectories as a checkpoint graph by identifying checkpoints that requires observation and cross-trajectory paths that can safely access the checkpoints from different trajectories. We have shown that the co-observation planning problem across different trajectories can be transformed into a multi-flow problem on the graph, and that we can find the minimal number of robot needed to finish the co-observation task.

While this work consider only the high-level path planning, the assignment of the duties within the sub-team can performed dynamically making it more difficult for attackers to successfully plan and execute attacks.

@@

{\small
\bibliographystyle{unsrt}
\bibliography{ADMM_planning,ACC,tron,ziqi,reachability}
}
